A quantitative framework for investigating the reliability of empirical network construction

### 2019-01-24 manuscript/reply_to_reviewers.tex

		\begin{refquote}
		It's a bit confusing to lead the reader towards a Bayesian analysis, and then immediately start with the MLE estimate. Why is this needed at all? (L162-186). Just start at 187?
		\end{refquote}

		\textbf{R:} The MLE estimate is part of the Bayesian framework as it dictates the shape of the distribution that we use. Moreover, it helps to formalise our argument that most networks are undersampled, justifying the Bayesian approach and the use of priors to reduce/set bounds around the resulting uncertainty. We therefore feel that it is important to keep some discussion of the MLE estimate in the manuscript. We now introduce the MLE formally within this context (lines 178-184) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (caption of Figure S2, \emph{Appendix S2}).

		Lines 178-184:

		\begin{quotation}
			The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda_{ij}$ can be computed from the number of observed interactions $k_{ij}$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$. The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution: ...
		\end{quotation}

@@

		\begin{quotation}
		    The shape parameters, or hyperparameters, may be set to particular values or derived from data (see below). They may be the same for all interactions, allowed to vary independently across interactions, or incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
		\end{quotation}

		Lines 251-259:

		\begin{quotation}
			Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx2017}). This would result in a highly informative prior that would, moreover, account for some of the non-independence in interaction probabilities.

	        Using an informative prior tailors the level of uncertainty surrounding each interaction and may account for non-independence of interactions (as in abundance-based or KNN models).
	    \end{quotation}

@@

		\end{refquote}

		\textbf{R:} We believe that this comment stems from a lack of clarity about the goal of our model. It is not designed to separate the three levels of uncertainty or introduce parameters at particular levels. The only inputs are a prior distribution, which could refer to any level of uncertainty applicable to the study at hand, and post-hoc counts of interactions and co-occurrences. Using only the observed data, it is impossible to separate the three levels of uncertainty and our model does not aim to do so (as stated in lines 159-165 and lines 198-200). We therefore do not believe that an in-depth discussion of identifiability would add much value to the manuscript and, in the interest of space, have decided not to include one. Instead, we refer interested readers to~\citet{Weinstein2017} which does attempt to separate sources of uncertainty.

		Lines 159-165:

		\begin{quotation}
			When considering a metaweb, we wish to separate unobserved interactions where $L_{ij}=0$ (unfeasible interactions) from interactions which were feasible but did not occur during sampling or were not detected (Fig. 1). An empirical ecologist will measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences. Given this information, how can we reduce the uncertainty around our estimated interaction probability?
		\end{quotation}

@@

	10. l.252: not clear. Why this choice?

		\textbf{R:} We have expanded the description of the reasoning behind our choice of prior and hope that the following is clearer:

		Lines 321-326:

		\begin{quotation}
			As we lack a trait-based model or similar published network, we use data from a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset to inform our prior distribution. This simulates an empirical Bayes model using a pilot site to inform the prior distribution. A site in the middle of the geographic distribution was selected in order to minimise bias towards species at any geographic extreme.
		\end{quotation}

@@

	3. Introduction of the case study seems off-topic and illogical.

		\begin{refquote}
		3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
		\medskip
		Line 240.  I found the justification for the system a bit odd.  Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?  At this point the reader is confused about the goal...
		\medskip
		Line 249.  The statement about training data is redundant with what is stated above – adjust writing.
		\end{refquote}

		\textbf{R:} We have now expanded our introduction of the case study (beginning line 302) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions. This relates back to our point that urging increased sampling effort is not likely to solve problems of uncertainty as long as sampling is limited in the number of methodologies that can be applied, biased towards abundant or easy-to-identify species, restricted to particular spatial sites and/or environmental conditions (if the network is intended to be more general), or all of the above. Given budgetary constraints, it is extremely likely that empirical ecologists cannot sample as intensively and extensively as they would like and therefore some uncertainty is likely to remain. We repeat this point in the discussion to ensure that the case study is relevant. We have also clarified our statement that a strict application of Bayesian statistics does not allow empirical priors, but that they are an option for researchers that are more concerned about matching their prior to their study system than with strict formalism (lines 293-296). As Reviewer 1 points out, this is somewhat controversial and we feel it is important to note the potential objection.

		\begin{quotation}
		  \textbf{Empirical example}

		     To illustrate the process of constructing a Bayesian network to quantify uncertainty about interactions, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (\emph{Appendix S5}). 
		      The high spatiotemporal resolution of this dataset makes it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig. 2). Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb. 
		      % To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. 
		      We calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda_{ij}$). We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S6} for \emph{Salix}-galler results).
		\end{quotation}

### 2019-01-24 manuscript/CI_interactions.tex
turned line numbers back on
all ready to resubmit after Dom's ok

\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{2}$, Kate Wootton$^{2}$, Dominique Gravel$^{3}$}
\date{
% \begin{minipage}[h]{0.6\textwidth}
\small$^1$ Department of Physics,\\
Chemistry and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
\medskip
\small$^2$ Department of Ecology\\ 
P.O. Box 7044\\ 
Swedish University of Agricultural Sciences \\ 
SE-750 07 Uppsala, Sweden\\
\medskip
\small$^3$ D\'{e}partement de biologie\\ 
Universit\'{e} de Sherbrooke\\ 
Sherbrooke, Canada
\medskip
\small$^\dagger$ Corresponding author:\\
alyssa.cirtwill@gmail.com\\
\medskip
\medskip
\normalsize Running head: Constructing quantitative interaction networks
% tel: +46 723 158464\\
% $^\ddagger$ anna.eklof@liu.se\\
% $^\star$ tomas.roslin@slu.se\\
% $^\diamond$ kate.wootton@slu.se\\
% $^\triangleright$ dominique.gravel@usherbrooke.ca
}

@@

% \begin{minipage}[h]{0.6\textwidth}
% \begin{itemize}
% \item Running title: Quantitative network construction
% \item Number of references: 37
% \item Number of figs, tables, \& text boxes: 4 % Limit is 10
% \end{itemize}
% \end{minipage}\begin{minipage}[h]{0.4\textwidth}
% \begin{itemize}
% \item Abstract word count: 290
% \item Main text word count: 6993, excluding abstract % Limit is 6000-7000 including figs, tables, references. 
% \end{itemize}
% \end{minipage}
% }

@@

          Fundamentally, some interactions are feasible while others are not~\citep{Poisot2015}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$ given some function describing trait matching $\mathbf{T_{ij}}$ as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. In some cases the traits prohibiting an interaction are known and there will be little uncertainty about $\lambda_{ij}$. Generally, however, the traits that might prohibit an interaction are unknown~\citep{Dormann2017} and uncertainty about $\lambda_{ij}$ will be high. 
          An unobserved interaction may have $\lambda_{ij}>0$, and the associated zero in an interaction matrix might be false. Using a trait-matching model can reduce uncertainty about $\lambda_{ij}$~\citep{Jordano2016}. As these models improve, $\lambda_{ij}$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. This leaves some uncertainty about whether some species pairs could interact.

@@

    When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which were feasible but did not occur during sampling or  were not detected (Fig.~\ref{conceptual_fig}). An empirical ecologist will measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences. Given this information, how can we reduce the uncertainty around our estimated interaction probability?

    One obvious way to reduce uncertainty is to increase sampling. High sample sizes will reduce uncertainty about the upper bound of $\lambda_{ij}$ and increase the probability of detecting unlikely or cryptic interactions (where $L_{ij}=1$ but $\chi_{ij}$ or $\delta_{ij}$ is low). In some systems, targeted sampling of particular species pairs could reduce especially high uncertainties about $\lambda_{ij}$, but this will not be possible everywhere (e.g., in host-parasitoid systems where parasitoid identities are unknown during sample collection). High-quality sampling is crucial in studies of empirical networks, but there are limits to the ability of sampling to reduce uncertainty (\emph{Appendix S2, Fig. S2}). As a complement to improved sampling, we can also reduce uncertainty by leveraging prior knowledge about the system using a Bayesian approach, as detailed below.

@@

        Alternatively, one can develop a prior based on the properties of a set of published networks (i.e., ``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}). This type of prior entails only one assumption: that the focal network has similar structural properties to those of published networks. For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks. The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network. If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:

@@

  \section*{An empirical example}

@@

        To treat each interaction as a Bayesian probability, we will combine the observed data with a distribution based on prior information. As we lack a trait-based model or similar published network, we will use data from a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset to inform our prior distribution. This simulates an empirical Bayes model using a pilot site to inform the prior distribution. A site in the middle of the geographic distribution was chosen in order to minimise bias towards species at any geographic extreme. To demonstrate how a poor choice of prior can give unreasonable posterior distributions, we repeated our analyses using priors derived from a much smaller system (\emph{Appendix S7}).

        To obtain priors, we estimated interaction frequencies based on the normalised degree of each species (see \emph{Appendix S8} for details and code). Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda_{ij}$. For species without observed interactions ($n=0$), the posterior distribution is identical to the prior distribution. For species where $n>0$, we can update the prior distribution with data. If we consider only pairs of species which were observed co-occurring but not interacting, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha_{ij}'$=$\alpha_{ij}$ and $\beta_{ij}'$=$\beta_{ij} + n_{ij}$. We calculated posterior distributions and 95\% credible intervals (function ``credible\_interval";~\emph{Appendix S9}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.

        Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many observations are necessary to be confident that two co-occurring species do not interact (note that the beta distribution can never equal 0 or 1). The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. We calculated the number of samples required to reach 95\% confidence that $\lambda_{ij}$ was below thresholds of 0.1, 0.05, and 0.01 as examples (function ``samples\_for\_threshold";~\emph{Appendix S9}). Finally, we may be interested in measures of network structure rather than the network itself. We can use posterior distributions of interactions to generate plausible ``true'' networks that would be obtained if sampling uncertainty could be eliminated and use these networks to estimate many network properties (worked example in \emph{Appendix S10}).

@@

% \captionsetup{singlelinecheck=false, font={stretch=2}}

@@

  \begin{figure}[h!]
    \caption{Nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that truly occur. Some feasible interactions (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits. For example, lions are less likely to predate upon elephants than zebras. If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to be lion prey and assign this interaction a probability of 0.\\
    \indent Interactions occur with different probabilities in any given sample. We show six example networks representing interactions observed over two days at three sites. Interactions which occur during fewer sampling days are less likely to be observed.\\
    \indent Not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be observed.\\
    \indent After combining these layers of uncertainty, some interactions which truly occur are very unlikely to be observed. The observed matrix (bottom) is a subsample of the true matrix where the probability of observing each interaction depends upon multiple layers of uncertainty. Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not. For an illustration of the way in which these levels of uncertainty combine in simulated data, and the effects of uncertainty on network structure, see \emph{Appendix S1}. Attributions for images are given in \emph{Appendix S1-A}.}
    \label{conceptual_fig}
    \begin{center}
    \includegraphics*[height=.45\textheight]{figures/conceptual_fig.eps}
    % \includegraphics*[height=.5\textheight]{Figure_1.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
      \caption{Despite the high replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that co-occurred rarely interacted. \textbf{A)} Histogram of the number of pairs of species observed co-occurring at least once. 9794 galler-enemy pairs were never observed co-occurring (not shown).
      \textbf{B)} Histogram of the number of observed interactions between co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} For each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship.}
      \label{histograms}
      \begin{center}
      \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      % \includegraphics*[height=.6\textheight]{Figure_2.eps}
      \end{center}
      \end{figure}

@@

  \begin{figure}[h!]
    \caption{Posterior distributions for the interaction probability ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$), based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}. Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly. It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda_{ij}<0.10$ but over 100 co-occurrences to be 95\% confident that $\lambda_{ij}<0.01$.}
    \label{Salix_pdfs_cdfs}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
    % \includegraphics*[width=.8\textwidth]{Figure_4.eps}
    \end{center}
    \end{figure}

>>>>

\author{Alyssa R. Cirtwill$^{1,2\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{3}$, Kate Wootton$^{3}$, Dominique Gravel$^{4}$}
\date{
% \begin{minipage}[h]{0.6\textwidth}
\small$^1$ Department of Physics,\\
Chemistry and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
\medskip
\small$^2$ Current address: Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
Stockholm, Sweden\\
\medskip
\small$^3$ Department of Ecology\\ 
P.O. Box 7044\\ 
Swedish University of Agricultural Sciences \\ 
SE-750 07 Uppsala, Sweden\\
\medskip
\small$^4$ D\'{e}partement de biologie\\ 
Universit\'{e} de Sherbrooke\\ 
Sherbrooke, Canada
\medskip
\small$^\dagger$ Corresponding author:\\
alyssa.cirtwill@gmail.com\\
\medskip
\medskip
\normalsize Running head: Constructing quantitative interaction networks
% tel: +46 723 158464\\
% $^\ddagger$ anna.eklof@liu.se\\
% $^\star$ tomas.roslin@slu.se\\
% $^\diamond$ kate.wootton@slu.se\\
% $^\triangleright$ dominique.gravel@usherbrooke.ca
}

@@

% \begin{minipage}[h]{0.6\textwidth}
% \begin{itemize}
% \item Running title: Quantitative network construction
% \item Number of references: 37
% \item Number of figs, tables, \& text boxes: 4 % Limit is 10
% \end{itemize}
% \end{minipage}\begin{minipage}[h]{0.4\textwidth}
% \begin{itemize}
% \item Abstract word count: 290
% \item Main text word count: 6997, excluding abstract % Limit is 6000-7000 including figs, tables, references. 
% \end{itemize}
% \end{minipage}
% }

@@

          Fundamentally, some interactions are feasible while others are not~\citep{Poisot2015}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$ given some function describing trait matching $\mathbf{T_{ij}}$ as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. In some cases the traits prohibiting an interaction are known and there will be little uncertainty about $\lambda_{ij}$. Generally, however, the traits that might prohibit an interaction are unknown~\citep{Dormann2017} and uncertainty about $\lambda_{ij}$ will be high. 
          An unobserved interaction may have $\lambda_{ij}>0$, and the associated zero in an interaction matrix might be false. Trait-matching models can reduce uncertainty about $\lambda_{ij}$~\citep{Jordano2016}. As these models improve, $\lambda_{ij}$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. This leaves some uncertainty about whether some species pairs could interact.

@@

    When considering a metaweb, we wish to separate unobserved interactions where $L_{ij}=0$ (unfeasible interactions) from interactions which were feasible but did not occur during sampling or were not detected (Fig.~\ref{conceptual_fig}). An empirical ecologist will measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences. Given this information, how can we reduce the uncertainty around our estimated interaction probability?

    One obvious way to reduce uncertainty is to increase sampling. High sample sizes will reduce uncertainty about the upper bound of $\lambda_{ij}$ and increase the probability of detecting unlikely or cryptic interactions (where $L_{ij}=1$ but $\chi_{ij}$ or $\delta_{ij}$ is low). In some systems, targeted sampling could also reduce especially high uncertainties about $\lambda_{ij}$, but this will not be possible everywhere (e.g., in host-parasitoid systems where parasitoid identities are unknown during sampling). High-quality sampling is crucial in studies of empirical networks, but there are limits to the ability of sampling to reduce uncertainty (\emph{Appendix S2, Fig. S2}). As a complement to improved sampling, we can also reduce uncertainty by leveraging prior knowledge about the system using a Bayesian approach, as detailed below.

@@

        Alternatively, one can develop a prior based on the properties of a set of published networks (``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}). This type of prior entails only one assumption: that the focal network has similar structural properties to those of published networks. For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks. The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network. If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:

@@

  \section*{Empirical example}

@@

        To treat each interaction as a Bayesian probability, we combine observed data with a distribution based on prior information. As we lack a trait-based model or similar published network, we use data from a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset to inform our prior distribution. This simulates an empirical Bayes model using a pilot site to inform the prior distribution. A site in the middle of the geographic distribution was selected in order to minimise bias towards species at any geographic extreme. To demonstrate how a poor choice of prior can give unreasonable posterior distributions, we repeated our analyses using priors derived from a much smaller system (\emph{Appendix S7}).

        To obtain priors, we estimated interaction frequencies based on the normalised degree of each species (details and code in \emph{Appendix S8}). Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda_{ij}$. For species without observed interactions ($n=0$), the posterior distribution is identical to the prior distribution. For species where $n>0$, we can update the prior distribution with data. If we consider only pairs of species which were observed co-occurring but not interacting, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha_{ij}'$=$\alpha_{ij}$ and $\beta_{ij}'$=$\beta_{ij}+n_{ij}$. We calculated posterior distributions and 95\% credible intervals (function ``credible\_interval";~\emph{Appendix S9}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.

        Rather than credible intervals for a posterior distribution after collecting data, we be interested in the number of observations necessary to be confident that two co-occurring species do not interact (note that the beta distribution can never equal 0 or 1). The number of samples needed will depend on our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. We calculated the number of samples required to reach 95\% confidence that $\lambda_{ij}$ was below thresholds of 0.1, 0.05, and 0.01 as examples (function ``samples\_for\_threshold";~\emph{Appendix S9}). Finally, we may be interested in measures of network structure. We can use posterior distributions of interactions to generate plausible ``true'' networks that would be obtained if sampling uncertainty could be eliminated and use these networks to estimate many network properties (worked example in \emph{Appendix S10}).

@@

\captionsetup{singlelinecheck=false, font={stretch=2}}

@@

  \begin{figure}[h!]
    \caption{Nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that truly occur. Some feasible interactions (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits. For example, lions are less likely to predate upon elephants than zebras. If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to be lion prey and assign this interaction a probability of 0.\\
    \indent Interactions occur with different probabilities in any given sample. We show six example networks representing interactions observed over two days at three sites. Interactions which occur during fewer sampling days are less likely to be observed.\\
    \indent Not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be observed.\\
    \indent After combining these layers of uncertainty, some interactions which truly occur are very unlikely to be observed. The observed matrix (bottom) is a subsample of the true matrix where the probability of observing each interaction depends upon multiple layers of uncertainty. Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not. For an illustration of the way in which these levels of uncertainty combine in simulated data, and the effects of uncertainty on network structure, see \emph{Appendix S1}. Attributions for images are given in \emph{Appendix S1-A}.}
    \label{conceptual_fig}
    \begin{center}
    % \includegraphics*[height=.45\textheight]{figures/conceptual_fig.eps}
    % \includegraphics*[height=.5\textheight]{Figure_1.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
      \caption{Despite the high replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that co-occurred rarely interacted. \textbf{A)} Histogram of the number of pairs of species observed co-occurring at least once. 9794 galler-enemy pairs were never observed co-occurring (not shown).
      \textbf{B)} Histogram of the number of observed interactions between co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} For each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship.}
      \label{histograms}
      \begin{center}
      % \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      % \includegraphics*[height=.6\textheight]{Figure_2.eps}
      \end{center}
      \end{figure}

@@

  \begin{figure}[h!]
    \caption{Posterior distributions for the interaction probability ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$), based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}. Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly. It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda_{ij}<0.10$ but over 100 co-occurrences to be 95\% confident that $\lambda_{ij}<0.01$.}
    \label{Salix_pdfs_cdfs}
    \begin{center}
    % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
    % \includegraphics*[width=.8\textwidth]{Figure_4.eps}
    \end{center}
    \end{figure}

### 2019-01-24 manuscript/coverletter_revision.tex
all ready to resubmit after Dom's ok

% \usepackage[britdate]{canterbury-letter}
\usepackage[britdate]{LiU-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
% \usepackage[margin=10pt,font=small,labelfont=bf]{caption}

@@

\position{Postdoctoral fellow}
\department{Department of Physics, Chemistry, and Biology (IFM)}
\location{581 83 Link\"{o}ping, Sweden}
\cityzip{581 83 Link\"{o}ping, Sweden}
\telephone{}
\fax{}
\email{alyssa.cirtwill@liu.se}
\url{http://cirtwill.github.io}
\name{Dr. Alyssa R. Cirtwill}

@@

    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}. This manuscript is aimed squarely at the audiencce of \textbf{Methods in Ecology and Evolution}: ecologists in need of new tools for addressing topical questions in ecology and for recognizing key limitations and caveats in their research. Thus, the goals of this manuscript are to demonstrate the extreme difficulty of observing all interactions that occur within a community and, given this difficulty, to provide a way forward: a framework for combining prior knowledge about the system with observed data in order to gauge the probability of interactions which were not observed. We close by offering concrete recommendations that will facilitate researchers' efforts to acknowledge and set bounds on the uncertainty inherent in ecological data.

    % We argue that, because of multiple levels of uncertainty surrounding interactions between species, the set of observed interactions will almost certainly be a subset of the interactions that can occur in a community. Interactions may not be observed because a species is rare and does not encounter its partner during sampling, because environmental constraints prohibit the interaction during sampling, because one or both species is difficult to observe in the field, or because the interaction truly does not occur. We emphasise that some of these sources of uncertainty can be reduced with increased sampling but that, because it is easier to observe species than interactions between species, increased sampling will tend to add more unobserved than observed interactions to a matrix. We illustrate the problem using an extensively-sampled, spatially-replicated \emph{Salix}-galler-natural enemy system (Kopelke \emph{et al.}, 2017. \textbf{Ecology} 98: 1730).

    % In many cases, it will not be feasible to sample all species pairs intensively enough (tens of observations per pair) to be confident that the pair does not interact. Given the time and resource constraints that often restrict fieldwork, we suggest that researchers supplement observed data with prior information about the system. Thus, they can set bounds on the probability of interaction between species that were not observed interacting. We demonstrate this simple Bayesian framework, including the selection of a prior distribution, and use it to predict the likely set of feasible interactions in our example \emph{Salix} system. Based on this framework, we close with a set of recommendations for both empiricists and theoreticians that should improve our ability to deal with the uncertainty inherent in ecological networks and compare networks across systems.

    As our central approach to this topic, we use a simple Bayesian framework. We are aware that there are several studies already using various forms of Bayesian networks to treat interactions as probabilities. These efforts are, however, generally confined to fairly theoretical work. We believe that empirical ecologists will find Bayesian interaction probabilities to be a useful tool when planning field sampling and when describing and analysing their focal communities. Our goal with this manuscript is, therefore, to introduce a Bayesian line of thought in as approachable and broadly-applicable terms as possible. To that end, we provide simple R code that illustrates each step of our approach.

    We have uploaded an earlier version of this manuscript to biorXiv \\(doi: \emph{https://doi.org/10.1101/332536}). The present version has been substantially re-organized and contains additional material not included in the pre-print.

    We hope that the general nature of uncertainty around interactions, as well as the broadly-applicable solution we offer, will be of interest to the readership of \textbf{Methods in Ecology and Evolution}. We are confident that our worked example and easy-to-use scripts will provide a useful template for empiricists and theoreticians alike. We hope that you agree and eagerly await your reply.

>>>>

% \usepackage[britdate]{canterbury-letter}
\usepackage[britdate]{SU-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
% \usepackage[margin=10pt,font=small,labelfont=bf]{caption}

@@

\position{Postdoctoral fellow}
\department{Department of Ecology, Environment, and Plant Sciences (DEEP)}
\location{Stockholm University}
\cityzip{Stockholm, Sweden}
\telephone{}
\fax{}
\email{alyssa.cirtwill@liu.se}
\url{http://cirtwill.github.io}
\name{Dr. Alyssa R. Cirtwill}

@@

    My co-authors and I are pleased to resubmit our manuscript 
    MEE-18-07-452:  \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}. Dr. Aaron Ellison, Senior Editor, noted that the Associate Editor and four reviewers ``\emph{recognise a kernel of important work in this manuscript}" but that a significant shift in emphasis was necessary for this kernel to shine through. We believe that this revision has addressed the Associate Editor's and Reviewers' concerns and that our manuscript is clearer and more polished as a result. We thank them for their careful feedback.

    Note that we uploaded an earlier version of this manuscript to biorXiv \\(doi: \emph{https://doi.org/10.1101/332536}). We have uploaded a copy of this version as CI\_preprint.pdf. The present version has been substantially re-organised and contains additional material not included in the pre-print.

    We appreciate the opportunity to resubmit our manuscript and thank you for your continued consideration. We remain confident that our manuscript will be of broad interest to the readers of \textbf{Methods in Ecology and Evolution} because of the general nature of uncertainty around interactions and the broadly-applicable solution we offer. We are confident that our worked example and easy-to-use scripts will provide a useful template for empiricists and theoreticians alike. We hope that you agree and eagerly await your reply.
